\documentclass[10pt,letter,roman]{moderncv}

\moderncvstyle{classic} 

\moderncvcolor{grey} 

\usepackage[scale=0.8, top=.8cm, bottom=.8cm]{geometry}

%remove comma from cventry
\renewcommand*{\cventry}[7][.25em]{%
  \cvitem[#1]{#2}{%
    {\bfseries#3}%
    \ifthenelse{\equal{#4}{}}{}{ {\slshape#4}}% 
    \ifthenelse{\equal{#5}{}}{}{, #5}%
    \ifthenelse{\equal{#6}{}}{}{, #6}%
    \ifx&#7&%
      \else{\newline{}\begin{minipage}[t]{\linewidth}\small#7\end{minipage}}\fi}}

% personal data
\firstname{Charles}
\familyname{Lee}
\address{715 Fountainhead Dr.}{San Leandro,CA 94578}   
\phone{+1~(510)~703~7958}                      
\email{lee.ch.ck@gmail.com}                         
\homepage{linkedin.com/in/charlescklee}                  

% ~~~~~ START
\begin{document}
\makecvtitle
\vspace*{-1.2cm}

\section{Education}
\vspace*{-.1cm}
\cventry{Sept 2008--\newline Dec 2012}{B.S. Chemical Engineering \textnormal\& B.S. Chemistry}{\newline University of California, San Diego (UCSD)}{La Jolla, CA.}{}{Double Major.  Minor in Political Science.  Provost Honors.} 
\cventry{Fall 2010}{Visiting Exchange Student in Chemical Engineering}{\newline University of Edinburgh}{Edinburgh, Scotland, United Kingdom.}{}{}

\vspace*{-.3cm}
\section{Engineering Projects}
\vspace*{-.1cm}
\cventry{Spring 2012}{Design of a Point-of-Care C-Reactive Protein Detection Device}{}{}{}{
\begin{itemize}
\item Designed two concepts for C-Reactive protein detection utilizing the bioanalytical assay ELISA on a lab-on-a-chip platform; a more accurate CD based test and a portable at-home test kit.
\item Produced CAD models of both designs and conducted calculated simulations towards their function.
\item Presented findings to classmates and colleagues through written proposals and oral presentations.
\end{itemize}}
\cventry{Winter 2012}{Toluene Hydrodealkylation Process Design}{}{}{}{
\begin{itemize}
\item Designed two stream processes for the production of benzene from toluene.
\item Produced process flow diagrams for both streams using ASPEN Plus.
\item Utilized Aspen Economic Analyzer to determine the more economically feasilby processes over a theoretical run of fifteen years.
\end{itemize}}

\vspace*{-.3cm}
\section{Relevant Coursework}
\vspace*{-.1cm}
\cventry{}{}{}{}{}{
\begin{itemize}
\item Introduction to Material Science (NANO 108)
\item Introduction to Nanotechnology (CENG 211) \& Nanomedicine (CENG 207)
\item Intermolecular and Surface Forces (CENG 212)
\item Synthetic Methods in Organic Chemistry (CHEM 152/252)
\item Mechanisms of Organic Reactions (CHEM 154/254)
\end{itemize}
}

\vspace*{-.3cm}
\section{Skills}
\vspace*{-.1cm}
\cventry{}{Laboratory Techniques}{}{}{}{
\begin{itemize}
\item Chemistry: organic and inorganic synthesis, filtration, solvent extraction, distillation, Infrared (IR) spectroscopy, Nuclear magnetic resonance (NMR) spectroscopy, chromatography (Thin Layer (TLC), liquid, gas (GC)) structural elucidation, schlenk lines, gloveboxes, FTIR, dynamic light scattering, titration, UV-vis spectrophotometry, metal catalytic reactions, polymerization.
\item Chemical Engineering: fuel cell simulation and analysis (use of COMSOL and MATLAB), plate heat exchanger efficiency, reverse osmosis membrane systems, process control systems, liposome nanoparticle synthesis.
\item General Engineering: digital oscilloscopes, function generators, multimeters, circuits, operational amplifiers.
\end{itemize}}
\cventry{}{Software}{}{}{}{ASPEN, ChemDraw, LabVIEW, Solidworks, AutoCAD, Adobe CS6, Mathematica, MATLAB, COMSOL. Windows 7, Linux, Mac OS X, \LaTeX.
}
\cventry{}{Programming Languages}{}{}{}{HTML, CSS, C, Python, MATLAB.
}

\vspace*{-.3cm}
\section{Experience}
\vspace*{-.1cm}
\cventry{Fall 2012}{UCSD Department of Nanoengineering}{\newline Tutor/Reader/Teaching Assisstant}{under Professor R. Herz}{}{Assisted in the development of the overall course structure for the first MATLAB course offered by the Department of Nanoengineering.  Held weekly tutorial sessions to supplement main lectures to ensure students understand MATLAB programming.}

\cventry{2008--Present}{American Institute of Chemical Engineers (AIChE)}{\newline Senior Advisor (2012), Webmaster (2011), Secretary (2010) of UCSD Chapter}{}{}{Advised and assisted other AIChE at UCSD officers in the planning and execution of club events.  Managed club membership information, records, and club website.}

\cventry{2008--2012}{Rotaract Club at UCSD}{\newline Service Chair (2010), Webmaster (2011)}{}{}{Led the planning and execution of community service projects and events.  Designed and created club website to inform members about club meetings and service projects.}

\vspace*{-.3cm}
\section{Additional Information \& Activities}
\vspace*{-.1cm}
\cvlistitem{Engineer in Training \#148756 - California Board for Professional Engineers, Land Surveyors, and Geologists, Feb 2013.}
\cvlistitem{International House UCSD 2011--2012}
%\cvlistitem{Open to Relocation}

\end{document}
